--- 
title: "Artifex - Fall 2022"
author: "David Reynolds"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
# output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: openscapes/series
description: "(Partial) course materials for Artifex, Fall 2022."
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(lubridate)
library(knitr)
```

# Course Overview - Artifex Fall 2022 {-}

Welcome to Artifex! The primary objective of this course/ club is to equip its members with the essential skills of a data scientist. The course delivery is a mix of lectures and project-based learning. The lectures will alternate between theory and tools. For the first half of the semester, the theory part of the course will be focused on linear regression and the tools part of the course will be related to R, R Studio, and Github. In the second half of the course, the theory will be focused on time series analysis and students will work in teams on a complex time series dataset hosted in Kaggle. 

## Prerequisites and Preparations {-}

- You should have some **basic knowledge** of R, and be familiar with the topics covered in the [Introduction to R](https://cengel.github.io/R-intro/).
- Have a recent version of [R](https://cran.r-project.org/) and [RStudio](https://www.rstudio.com/) installed. 
- Install and load the `tidyverse` package.

```{r, eval=FALSE, purl = FALSE}
install.packages("tidyverse")  
library(tidyverse)
```


## References {-}
Boehmke, Bradley C. (2016) Data Wrangling with R
http://link.springer.com/book/10.1007%2F978-3-319-45599-0

Grolemund, G & Wickham, H (2017): R for Data Science http://r4ds.had.co.nz

Wickham, H. (2014): Tidy Data https://www.jstatsoft.org/article/view/v059i10