--- 
title: "Artifex - Fall 2022"
author: "David Reynolds"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
# output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: openscapes/series
description: "(Partial) course materials for Artifex, Fall 2022."
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(lubridate)
library(knitr)
```

# Course Overview - Artifex Fall 2022 {-}

Welcome to Artifex! The primary objective of this course/ club is to equip its members with the essential skills of a data scientist by working through a real world business analytics project with an industry partner. The course delivery is a mix of lectures and project-based learning. The lectures will all be tailored to our project and will be more prevalent in the beginning of the course. All lecture materials will be posted on this website. Further details on the partner project are on the syllabus on Canvas.

## Prerequisites and Preparations {-}

- You should have some **basic knowledge** of R, and be familiar with the topics covered in the [Introduction to R](https://cengel.github.io/R-intro/).
- Have a recent version of [R](https://cran.r-project.org/) and [RStudio](https://www.rstudio.com/) installed. 
- Install and load the `tidyverse` package.

```{r, eval=FALSE}
install.packages("tidyverse")  
library(tidyverse)
```


## References {-}

Grolemund, G & Wickham, H (2017): R for Data Science http://r4ds.had.co.nz

Wickham, H. (2014): Tidy Data https://www.jstatsoft.org/article/view/v059i10